% Created 2021-08-31 Tue 03:29
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Andrew Hooke}
\date{\today}
\title{thing 1}
\hypersetup{
 pdfauthor={Andrew Hooke},
 pdftitle={thing 1},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section*{Chapter 1}
\label{sec:org113f903}
"You dunce. You absolute fucking dunce." James flicked his eraser in my direction, passing my head and bouncing off the wall behind me. \\
"I wasn't laughing at her, I was laughing at what she said, and to be honest, I don't really give a shit because I don't know who she --" the dorm president opened the door to the conference room, interrupting our discussion about last Saturday. James took this as a cue to get up from his chair, slowly, with his hands on his knees, and walk over to his previously flicked eraser. \\
"Good afternoon Ambassadors, hope your weekend went well." Student government types, the scum of the earth. Not really, but their sense of entitlement oozed from every word that came out of their mouth: always disingenuous, always as if they were trying out for a real political position. The Student Ambassadors were what you joined if you wanted a leadership role on your resume without actually vying for an elected position. The only thing preventing an influx of resume-padders is the lengthy application essay requirement, but if you could ham up your humblebragging entitlement and use enough buzzwords for a five-hundred word paragraph, you were a shoo-in. This was James and my last-ditch effort to getting some leadership brownie points before we graduate. As seniors, student government seems so fatuous, especially the uppity juniors and their "president" roles. \\
"Here is a summary of last month's expenses and our event schedule for this month," the president slid a stack of handouts down the table, I grabbed one for myself and one for James, who was just sitting back down in his seat. "You know the drill, ten minutes of budget brainstorming, we'll reconvene at three fifty\ldots{}" he glanced at his watch, "six. Begin." \\
I turned my attention back to James. "I don't know who she was, what little I can remember was she was blonde, and had a ponytail," I counted with my fingers to emphasize my faux-agression towards him. It's all a big game, really. Pretend to care about this, say you care about that. At the end of the day we both know I'd want nothing to do with the girl unless I knew her well enough, I wasn't one to sleep around. Another game of ours was to get as little work done as possible during these meetings, which we basically win at every time, never getting anything done. \\
"She said 'nice shirt' and you laughed at her." James said whispering, with a robotic staccato pacing, poking the table with his finger with each word, a small grin forming at his own dramatic performance. "If drunk you can't take up a chance to make a move, how do you expect sober you to get anywhere near that?" \\
"As it turns out, the handout has an error: the budget does not include the profits from the fundraiser last Friday, so just keep that in mind while you are discussing." Thanks for interrupting. \\
We finished the meeting with the typical "I think we did a pretty good job balancing the budget, but we could always save some money" conclusion and left the conference room, James and I the first to escape into the endless bookshelves on the library's fourth floor. \\
"This Friday, you guys are hosting a party, right?" James lived on campus, and had little access to parties due to the fact that all of his friends were seniors, and most were living off-campus. \\
"Yeah, Eric's idea\ldots{} he said his girlfriend is bringing her friends, so it shouldn't be so boring this time." This is a partial lie: Eric said "my woman is bringing a couple of her friends, so don't get grabby" to the housemates. This naturally expanded to include more guests than intended via a game of telephone with our outer ring of friends, with absolutely no reason in doing so. The natural tendency is to exaggerate, and when it comes to parties, that's half the fun. \\
"Stella, right? Yeah, I heard she's been spending a lot of time at UH, rumor has it she's cheating on Eric." We all already suspected this. She'd been getting handsy with a sophomore at a kickback a few weeks ago when Eric stayed home studying for an exam. Of course that sophomore wasn't at UH, but it showed enough proof of her willingness to submit to someone other than Eric. Naturally, he wouldn't take any of our words for it unless he saw it with his own eyes. \\
Needless to say, I was excited for the weekend. \\
\section*{Chapter 2}
\label{sec:orgb5bbd27}
\end{document}